\documentclass[a4paper, 11pt]{article}
\usepackage[a4paper, top=1.3cm, bottom=1.3cm, left=2cm, right=2cm]{geometry}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

%\usepackage{ragged2e


\usepackage{graphicx} % Required for inserting images
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{anyfontsize}
\usepackage[explicit]{titlesec}
\usepackage{ifthen}
\usepackage{etoolbox}
%\usepackage{stringstrings}


\include{bibpreambule}



\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\pagestyle{empty}

\include{color-size}

\newcommand{\email}[1]{\href{mailto:#1}{\textcouleursecondaire{#1}}}


\newcommand{\familyname}{Van Biesbroeck}
\newcommand{\givenname}{Antoine}

\newcommand{\nom}{\givenname~\familyname}
\newcommand{\adresse}{Centre Borelli - ENS Paris-Saclay\\
91190 Gif-sur-Yvette\\
France}
%\newcommand{\coordonnes}{\email{antoine.van-biesbroeck@polytechnique.edu}\newline 06 \newline \href{https://www.linkedin.com/in/antoine.van-biesbroeck}{linkedin.com/in/antoine.van-biesbroeck}}

\newcommand{\titre}{Assistant professor}
\newcommand{\intro}{Research in Bayesian statistics, sensitivity analysis and uncertainty quantification.}

\newcommand{\emailadress}{antoine.van\_biesbroeck@ens-paris-saclay.fr}
\newcommand{\tel}{000}
\newcommand{\link}{vbkantoine.github.io}
\newcommand{\linktarget}{https://vbkantoine.github.io}

\forcsvlist{\listadd\coordonnes}{\emailadress,\newline,\link}

\include{items}



\author{\nom}
\title{CV-\nom}
\hypersetup{hidelinks, pdfauthor=\nom, pdftitle=CV-\nom}


\begin{document}



\forlistloop{\addlength}{\coordonnes}

\parbox{\linewidth}{\fontsize{\HUGEtext}{\HUGEbase}\selectfont\bfseries\textcouleurprimaire{\nom}}
\vaststretchs{2}
% \rule{\descriptionpar}{2pt}\\[2em]
% \rule{\indentdescription}{2pt}\\[2em]
% \hfill\rule{\rightbox}{2pt}\\
% \forlistloop{\printlinerightbox}{\coordonnes}

\begin{minipage}{\linewidth}
    \parbox{0.35\linewidth}{\fontsize{\NORMALtext}{\NORMALbase}\selectfont\neutresecondaire\adresse}\hfill
         \parbox{\rightbox}{%
            \forlistloop{\trueprintlinerightbox}{\coordonnes}%
        }%
\end{minipage}
\vaststretchs{2.5}

\hspace*{\indentsubtitre}%
\begin{minipage}{\parsubtitre}%
    \hspace*{\indentsubtitre}{\fontsize{\NORMALtext}{\NORMALbase}\selectfont\couleursecondaire\titre}\\[-2pt]
    {\fontsize{\INTERtext}{\INTERbase}\selectfont\neutresecondaire\intro}%
\end{minipage}
\vaststretchs{2}

\section*{Professional experience}

\mainitem{Since 2025}{Assistant professor}{ENS Paris-Saclay (France)}{Research in Bayesian statistics, sensitivity analysis and uncertainty quantification at Centre Borelli.}

\mainitem{2022-2025}{Research associate}{CEA Paris-Saclay (France)}{Research on Bayesian learning for seismic risk assessment studies in the nuclear industry.}

\mainitem{2021-2022}{Data Scientist}{EDF China, Beijing (China)}{Research \& Development on Machine Learning projects within the Digital Innovation team of EDF China.}

\mainitem{2021}{Research intern in Bayesian statistics}{CEA Paris-Saclay (France)}{Research subject: `Objective prior construction for Bayesian estimation of seismic fragility curves'.}

\mainitem{2019}{Research intern in Deep Learning}{Institute of Industry and Sciences, Guangzhou (China)}{Research subject: `Surface mesh generation based on segmentation via Deep Learning'.}

%\mainitem{2018}{Research intern in applied mathematics}{CMLA, Cachan (France)}{Research subject: `Systemic risk control in financial networks'.}

\section*{Education}

\mainitem{2022-2025}{PhD}{Ecole Polytechnique, Palaiseau (France)}{Thesis subject: `Extended reference prior theory for objective and practical inference, application to robust and auditable seismic fragility curves estimation'. Supervised by Josselin Garnier. Collaboration with CEA (French atomic energy commission).}

\mainitem{2020-2021}{Master's degree MVA}{Université Paris-Saclay, Gif-sur-Yvette (France)}{Master's degree `Mathématiques Vision Apprentissage'. Training in applied maths to statistical learning.}

\mainitem{2017-2021}{Normalien}{ENS Paris-Saclay (France)}{%
4 years graduate program which aims at training high level researchers in sciences.\\
(2020) Laureate of the `agregation' competitive examination in mathemetics, ranked 3rd.}

\mainitem{2014-2017}{Classes préparatoires}{Lycées Daudet \& Champollion, Nîmes \& Grenoble (France)}{%
Post-secondary intensive program in sciences to pass competitive examination for graduate schools.
}


%\compritem{2014}{High School diploma}{Lycée Saint-Stanislas, Nîmes (France)}


\section*{Teaching}

\newlength{\courses}
\settowidth{\courses}{\fontsize{\SUBtext}{\SUBbase}\selectfont\itshape\textcouleursecondaire{Courses: }}

%\mainitem{2022-2024}{Teaching assistant in mathematics}{Ecole Polytechnique, Palaiseau (France)}{Courses: Introduction to probability \& statistics (Bachelor of Science program, 2nd year);\\ \hspace*{\courses}Introduction to python (Engineer program, 1st year);\\ 
%\hspace*{\courses}Measure and integration theory (Bachelor of Science program, 3rd year).\\
%\hspace*{\courses}Mathematical foundation of Data Science (Master of Science program, 1st year).}

\compritem{Since 2025}{Assistant professor in mathematics}{ENS Paris-Saclay (France)}

\compritem{2022-2025}{Teaching assistant in mathematics}{Ecole Polytechnique, Palaiseau (France)}

\compritem{2019-2021}{Examiner in mathematics}{Lycée Saint-Louis, Paris (France)}

\section*{Publications}% \& conférences}

%\subsection*{Regular papers}
\nocite{*}

\printbibliography[type=article, heading=subsection, title=Regular papers]


\printbibliography[type=inproceedings, heading=subsection, title=Proceedings, notkeyword={conf}]


\printbibliography[type=inproceedings, heading=section, title=Contributions in international conference, keyword={inter}] %filter=conf]


%\printbibliography[type=inproceedings, heading=section, title=Contributions in main national conferences, keyword={nat}]


%
%
\section*{Grants and awards}
%
\compritem{2024}{ISBA travel award}{The International Society for Bayesian Analysis}
%
\compritem{2024}{ISAS best oral award}{%Institut des sciences appliquées et de la simulation pour les énergies bas carbone  Institute of Applied Sciences and Simulations for low carbon energies, 
Science days of ISAS, CEA (French atomic energy commission)}
%
\compritem{2024}{SIAM student travel award}{Society for Industrial and Applied Mathematics}
%
%
\compritem{2022}{CFR grant for doctoral studies}{CEA (French atomic energy commission)}
%
%
\compritem{2017}{Normalien civil servant grant}{ENS Paris-Saclay}
%
%
\section*{Additional skills}
%
\persitem{Programming}{\fontsize{\SUBtext}{\SUBbase}\selectfont%
    \textneutreprimaire{Proficiency in \textbf{LaTex} and \textbf{Python}.}}
%
\persitem{Languages}{\fontsize{\SUBtext}{\SUBbase}\selectfont%
    \textneutreprimaire{\textbf{French} (Native), \textbf{English} (Cambridge Advanced English grade C), \textbf{Chinese} (Notions).}}
%
%
%
\section*{Involvement}
%
\persitem{2024-2025}{\fontsize{\SUBtext}{\SUBbase}\selectfont%
    \textneutreprimaire{PhD student representative at the CMAP lab council.}}
%
\persitem{2023-2024}{\fontsize{\SUBtext}{\SUBbase}\selectfont%
    \textneutreprimaire{PhD student representative at the EDMH doctoral school council.}}
%
\persitem{Since 2020}{\fontsize{\SUBtext}{\SUBbase}\selectfont%
    \textneutreprimaire{Co-founder and vice president of the Delaney Automobile Club.}}
%
%\end{minipage}%
%}





\end{document}
